Implications of uniformly distributed, empirically informed priors for phylogeographical model selection: A reply to Hickerson et al.

### 2014-02-26 manuscripts/reply/reply.tex
Updating Jeet's address on reply ms.
Updating acknowledgements of reply ms.
Updating authors and acknowledgements for reply ms.

\author[1]{Jamie R.\ Oaks\thanks{Corresponding author: \href{mailto:joaks1@gmail.com}{\tt joaks1@gmail.com}}\thanks{Current address: Department of Biology, University of Washington, Seattle, Washington 98195}}
\author[2]{Jeet Sukumaran}
\author[3]{Charles W.\ Linkem}
\author[4]{Cameron D.\ Siler}
\author[1]{Rafe M.\ Brown}
\affil[1]{Department of Ecology and Evolutionary Biology, University of Kansas, Lawrence, Kansas 66045}
\affil[2]{Department of Biology, Duke University, Durham, North Carolina 27708}
\affil[3]{Department of Biology, University of Washington, Seattle, Washington 98195}
\affil[4]{Sam Noble Museum, Department of Biology, University of Oklahoma, Norman, Oklahoma 73072}

@@

\section{Acknowledgments}
We thank Melissa Callahan, Jake Esselstyn, Mark Holder, Emily McTavish, Daniel
Money, Jordan Koch, and Adam Leach\'{e} for insightful comments that greatly
improved this work.
J.\ Oaks thanks the National Science Foundation for supporting this work (DEB
1011423 and DBI 1308885).
J.\ Oaks was also supported by the University of Kansas (KU) Office of Graduate
Studies, Society of Systematic Biologists, Sigma Xi Scientific Research
Society, KU Department of Ecology and Evolutionary Biology, and the KU
Biodiversity Institute.
We also thank Mark Holder, the KU Information and Telecommunication Technology
Center, KU Computing Center, and the iPlant Collaborative for the computational
support necessary to conduct the analyses presented herein.

@@

\section*{Supporting Information}
% PUT MAIN TEXT CITATION HERE
\hangindent=1cm
Oaks, J.~R., J.~Sukumaran, C.~W.\ Linkem, C.~D.\ Siler, and R.~M.\ Brown. \msTitle.

>>>>

\author[1]{Jamie R.\ Oaks\thanks{Corresponding author: \href{mailto:joaks1@gmail.com}{\tt joaks1@gmail.com}}\thanks{Current address: Department of Biology, University of Washington, Seattle, Washington 98195}}
\author[2]{Charles W.\ Linkem}
\author[3]{Jeet Sukumaran}
\affil[1]{Department of Ecology and Evolutionary Biology, University of Kansas, Lawrence, Kansas 66045}
\affil[2]{Department of Biology, University of Washington, Seattle, Washington 98195}
\affil[3]{Department of Ecology and Evolutionary Biology, University of Michigan, Ann Arbor, Michigan 48109}

@@

\section{Acknowledgments}
We thank Melissa Callahan, Jake Esselstyn, Cameron Siler, Mark Holder, Rafe
Brown, Emily McTavish, Daniel Money, Jordan Koch, and Adam Leach\'{e} for
insightful comments that greatly improved this work.
We thank Michael Hickerson and co-authors for generously providing their data.
J.\ Oaks and C.\ Linkem thank the National Science Foundation for supporting
this work (DEB 1011423, DBI 1308885 and BIO-1202754).
J.\ Oaks was also supported by the University of Kansas (KU) Office of Graduate
Studies, Society of Systematic Biologists, Sigma Xi Scientific Research
Society, KU Department of Ecology and Evolutionary Biology, and the KU
Biodiversity Institute.
We also thank Mark Holder, the KU Information and Telecommunication Technology
Center, KU Computing Center, and the iPlant Collaborative for the computational
support necessary to conduct the analyses presented herein.

@@

\section*{Supporting Information}
% PUT MAIN TEXT CITATION HERE
\hangindent=1cm
Oaks, J.~R., C.~W.\ Linkem, and J.~Sukumaran. \msTitle
